Knowledge \& the web: exercise session 6

### 2015-11-22 exercise_6/ex6.tex
accuracy

We conclude this report with a brief summary of our results and our conclusion about the methods.
In following table we give the accuracy, precision and recall of our best configuration.
With \emph{accuracy} we mean the retrieved instances 
From these scores we decided what was in our opinion the best method.

>>>>

We conclude this report with a brief summary of our results and our conclusion about the methods.
In following table we give the accuracy, precision and recall of our best configuration.
With \emph{accuracy} we mean the proportion of true results (both true positives and true negatives) among the total number of cases examined.
For the Titanic case this would mean:
$$accuracy = \frac{\#\text{true dead} + \#\text{true alive} }{\#\text{true dead} + \#\text{false dead} + \#\text{true alive} + \#\text{false alive}}$$
From these scores we decided what was in our opinion the best method.
